Edge sign prediction in general graphs and Correlation Clustering

### 2017-09-14 troll/introduction.tex
small clarification to the first batch algo
add two refs

With this definition of social networks, we now look at how the learning problem of \esp{} can be
used in real world applications. More precisely, we present four possible applications, and order
them by how severely negative interactions impact the well-being of users of the networks.
First, it could help improve the quality of link recommendation in solely positive networks. Such
networks indeed contain implicit negative links~\autocite{Yang2012}. By asking users to label a
small proportion of existing links as truly positive or actually negative, recommended links could
be discarded if they are predicted to be negative.
%
Second, this could be used to monitor news textual comments in a scalable fashion and thus ensure
that online debates remain courteous and constructive. For instance, \textcite{betterDebate14} show
that by visually reminding comment authors of the importance of respecting the plurality of
opinions, the quality of debates is improved (other references can be found
in~\autocite{journalism15}).
%
Third, like many other fields, human resource management is undergoing a transformation through the
increasing use of Machine Learning~\autocite{MLinHR16}. Among other tools, assessing personal
relationships between employees is crucial to maintain a productive work environment. Whereas this
can be done by invasive wearable sensors~\autocite{WearableBehavior09}, our methods could predict
which employees would form the tighter teams from a small amount of labeled data.
%
Fourth, and most critical, predicting the sign of interactions could be a tool to detect users with
a high proportion of negative interactions. Indeed, because people tend to be less inhibited in
their online interactions~\cite{Suler04}, some users may join an online community with the main goal
to disrupt it, by engaging into anti-social behavior and creating conflictual relationships with
other members. This kind of attitude expressed publicly on social media leads to the following
definition of \emph{trolls}: \enquote{users whose real intentions are to cause disruption and/or to
trigger or exacerbate conflict for the purposes of their own amusement}~\autocite{Hardaker10}.
\Textcite{Shachaf10} elaborate on their motives, adding that boredom, attention seeking, and
revenge motivate trolls; they find pleasure from causing damage to other people or to the community
as a whole. An extreme form of trolling is bullying (\ie{} the behavior of someone intentionally and
repeatedly harming a victim that is unable to defend himself or herself) and just like anything
else, it has an online version called cyber bullying~\autocite{cyberbullying13}. Such behavior is
rather widespread, one study revealing that 72\% of \np{1454} surveyed teenagers reported at least
one occurrence of cyberbullying, most of them through instant messaging~\autocite{Juvonen08}. While
we have not conducted experimental study on this topic, we believe that being able to predict such
harmful interactions would be beneficial for the majority of users.

@@

From the modeling and algorithmic viewpoints, because of the huge amount of available networked
data, a major concern in developing learning methods for \esp{} is algorithmic
scalability. Many successful, yet simple heuristics for \esp{} are based on the
troll-trust features, \ie{} on the fraction of outgoing negative links (trollness) and incoming
positive links (trustworthiness) at each node. We first define these notions and more notations in
\autoref{s:prel}, along with others tools and precise problem statements. Then we study such
troll-trust heuristics by defining in \autoref{s:gen} a probabilistic
generative model for the signs on the directed links of a given network. We also show that these
heuristics can be understood and analyzed as approximators to the Bayes optimal classifier for our
generative model. In this context, we design our first batch algorithm and show in
\autoref{s:algbatch} that it provably approximates the Bayes classifier on dense graphs.
We furthermore gather empirical evidence supporting our probabilistic model by observing
that a logistic model trained on trollness and trustworthiness features alone is able to learn
weights that, on all datasets considered in our experiments, consistently satisfy the properties
predicted by our model.

>>>>

With this definition of social networks, we now look at how the learning problem of \esp{} can be
used in real world applications. More precisely, we present four possible applications, and order
them by how severely negative interactions impact the well-being of users of the networks.
First, it could help improve the quality of link recommendation in solely positive networks. Such
networks indeed contain implicit negative links~\autocite{Yang2012}. By asking users to label a
small proportion of existing links as truly positive or actually negative, recommended links could
be discarded if they are predicted to be negative.
%
Second, this could be used to monitor news textual comments in a scalable fashion and thus ensure
that online debates remain courteous and constructive. For instance, \textcite{betterDebate14} show
that by visually reminding comment authors of the importance of respecting the plurality of
opinions, the quality of debates is improved (other references can be found
in~\autocite{journalism15}). In a more extreme case, banning users with aggressive and hateful
behavior has proved effective in the case of Reddit~\autocite{RedditBan15}.
%
Third, like many other fields, human resource management is undergoing a transformation through the
increasing use of Machine Learning~\autocite{MLinHR16}. Among other tools, assessing personal
relationships between employees is crucial to maintain a productive work environment. Whereas this
can be done by invasive wearable sensors~\autocite{WearableBehavior09}, our methods could predict
which employees would form the tighter teams from a small amount of labeled data.
%
Fourth, and most critical, predicting the sign of interactions could be a tool to detect users with
a high proportion of negative interactions. Indeed, because people tend to be less inhibited in
their online interactions~\cite{Suler04}, some users may join an online community with the main goal
to disrupt it, by engaging into anti-social behavior and creating conflictual relationships with
other members. This kind of attitude expressed publicly on social media leads to the following
definition of \emph{trolls}: \enquote{users whose real intentions are to cause disruption and/or to
trigger or exacerbate conflict for the purposes of their own amusement}~\autocite{Hardaker10}.
\Textcite{Shachaf10} elaborate on their motives, adding that boredom, attention seeking, and
revenge motivate trolls; they find pleasure from causing damage to other people or to the community
as a whole. An extreme form of trolling is bullying (\ie{} the behavior of someone intentionally and
repeatedly harming a victim that is unable to defend himself or herself) and just like anything
else, it has an online version called cyber bullying~\autocite{cyberbullying13}. Such behavior is
rather widespread, one study revealing that 72\% of \np{1454} surveyed teenagers reported at least
one occurrence of cyberbullying, most of them through instant messaging~\autocite{Juvonen08}. While
we have not conducted experimental study on this topic, we believe that being able to predict such
harmful interactions would be beneficial for the majority of users.

@@

From the modeling and algorithmic viewpoints, because of the huge amount of available networked
data, a major concern in developing learning methods for \esp{} is algorithmic
scalability. Many successful, yet simple heuristics for \esp{} are based on the
troll-trust features, \ie{} on the fraction of outgoing negative links (trollness) and incoming
positive links (trustworthiness) at each node. We first define these notions and more notations in
\autoref{s:prel}, along with others tools and precise problem statements. Then we study such
troll-trust heuristics by defining in \autoref{s:gen} a probabilistic
generative model for the signs on the directed links of a given network. We also show that these
heuristics can be understood and analyzed as approximators to the Bayes optimal classifier for our
generative model. In this context, we design our first batch algorithm and show in
\autoref{ss:bayes_approx} that it provably approximates the Bayes classifier on dense graphs.
We furthermore gather empirical evidence supporting our probabilistic model by observing
that a logistic model trained on trollness and trustworthiness features alone is able to learn
weights that, on all datasets considered in our experiments, consistently satisfy the properties
predicted by our model.
